QPLIB: A Library of Quadratic Programming Instances

### 2017-02-08 format.tex
further tiny clarifications and corrections

The data is in free format (blanks separate values), but must occur in
the order given here. Any blank lines, or lines starting with any of the
characters !, \% or \# are ignored. Each term in the first column of
Table~\ref{tab-qplib-format} denotes a required value. Any strings beyond
those required on a given line will be regarded as comments and ignored.
Real values may either by in decimal or exponential formats; for the latter,
the exponent may be preceded by either the character \texttt{D} or \texttt{E},
e.g. \texttt{12.56D+2} or \texttt{12.56E+2}. Variable and constraint indices
are \textbf{1-based}.

@@

sense & one of the words minimize or maximize (character string, case irrelevant) & \\

@@

$\sum_{i\in\Mcm} n^{Q^i}$ & number of nonzeros (integer) in lower triangles of
$Q^i$, sum up over all $i\in\Mcm$  & [2,4] \\

@@

$\sum_{i\in\Mcm} n^{b^i}$ & number of nonzeros (integer) in $b^i$, sum up over all $i \in \Mcm$ &

@@

{\small
\begin{verbatim}
! ---------------
! example problem
! ---------------
MIPBAND   # problem name
QML       # problem is a mixed-integer quadratic program
Minimize  # minimize the objective function
3         # variables
2         # general linear constraints
5         # nonzeros in lower triangle of Q^0
1 1 2.0   5 lines row & column index & value of nonzero in lower triangle Q^0
2 1 -1.0  |
2 2 2.0   |
3 2 -1.0  |
3 3 2.0   |
-0.2      default value for entries in b_0
1         # non default entries in b_0
2 -0.4    1 line of index & value of non-default values in b_0
0.0       value of q^0
4         # nonzeros in vectors b^i (i=0,...,m)
1 1 1.0   4 lines constraint, index & value of nonzero in b^i (i=0,...,m)
1 2 1.0   |
2 1 1.0   |
2 3 1.0   |
1.0E+20   infinity
1.0       default value for entries in c_l
0         # non default entries in c_l
1.0E+20   default value for entries in c_u
0         # non default entries in c_u
0.0       default value for entries in l
0         # non default entries in l
1.0       default value for entries in u
1         # non default entries in u
2 2.0     1 line of non-default indices and values in u
0         default variable type is continuous
1         # non default variable types
3 2       variable 3 is binary
1.0       default value for initial values for x
0         # non default entries in x
0.0       default value for initial values for y
0         # non default entries in y
0.0       default value for initial values for z
0         # non default entries in z
0         # non default names for variables
0         # non default names for constraints
\end{verbatim}
}

>>>>

The data is in free format (blanks separate values), but must occur in
the order given here. Any blank lines, or lines starting with any of the
characters !, \% or \# are ignored. Each term in the first column of
Table~\ref{tab-qplib-format} denotes a required value. Any strings beyond
those required on a given line will be regarded as comments and ignored.
Real values may either by in decimal or exponential formats; for the latter,
the exponent may be preceded by either the character \texttt{D} or \texttt{E},
e.g. \texttt{12.56D+2} or \texttt{12.56E+2}. Variable indices, $j$, must lie in
the range $1 \leq j \leq n$, while constraint indices, $i$, must satisfy
$1 \leq i \leq m$, that is they are both \textbf{one-based}. The case for
character strings is irrelevant.

@@

sense & one of the words minimize or maximize (character string) & \\

@@

$\displaystyle \sum_{i\in\Mcm} n^{Q^i}$ & number of nonzeros (integer) in lower triangles of
$Q^i$, summed over all $i\in\Mcm$  & [2,4] \\

@@

$\displaystyle \sum_{i\in\Mcm} n^{b^i}$ & number of nonzeros (integer) in $b^i$, summed over all $i \in \Mcm$ &

@@

{\small
\begin{verbatim}
! ---------------
! example problem
! ---------------
MIPBAND   # problem name
QML       # problem is a mixed-integer quadratic program
Minimize  # minimize the objective function
3         # variables
2         # general linear constraints
5         # nonzeros in lower triangle of Q^0
1 1 2.0   5 lines row & column index & value of nonzero in lower triangle Q^0
2 1 -1.0  |
2 2 2.0   |
3 2 -1.0  |
3 3 2.0   |
-0.2      default value for entries in b_0
1         # non default entries in b_0
2 -0.4    1 line of index & value of non-default values in b_0
0.0       value of q^0
4         # nonzeros in vectors b^i (i=1,...,m)
1 1 1.0   4 lines constraint, index & value of nonzero in b^i (i=1,...,m)
1 2 1.0   |
2 1 1.0   |
2 3 1.0   |
1.0E+20   infinity
1.0       default value for entries in c_l
0         # non default entries in c_l
1.0E+20   default value for entries in c_u
0         # non default entries in c_u
0.0       default value for entries in l
0         # non default entries in l
1.0       default value for entries in u
1         # non default entries in u
2 2.0     1 line of non-default indices and values in u
0         default variable type is continuous
1         # non default variable types
3 2       variable 3 is binary
1.0       default value for initial values for x
0         # non default entries in x
0.0       default value for initial values for y
0         # non default entries in y
0.0       default value for initial values for z
0         # non default entries in z
0         # non default names for variables
0         # non default names for constraints
\end{verbatim}
}
